---
title: "Project RAD's fixes week"
output: html_notebook
---

Loading in Data- Andrew
```{r}
library(tidyverse)
library(taigr)
prism <- load.from.taiga(data.name='prism-repurposing-20q2-5e60', data.version=5, data.file='primary-screen-replicate-collapsed-logfold-change')
prism_meta <- load.from.taiga(data.name='prism-repurposing-20q2-5e60', data.version=5, data.file='primary-screen-replicate-collapsed-treatment-info')
crispr <- load.from.taiga(data.name='public-21q2-110d', data.version=12, data.file='Achilles_gene_effect')
library(stats)
```

Creating the inhibitor coorelation table - Andrea, Rohan, Diana
```{r}
inhibitors <- prism_meta %>%
  dplyr::filter(str_detect(moa, "inhibitor")) #Filtering the prism meta data for only inhibitors

cell_lines <- intersect(rownames(prism), rownames(crispr)) #cell lines that are in both dependency and prism

#for july 19, we added the prism 4 code so that we are only looking at prism values that are less than 0. 
prism_overlap <- prism[cell_lines, inhibitors$column_name]
prism2 = prism_overlap<0
prism3 = prism2*prism_overlap
prism4 = na_if(prism3, 0) #making prism data that is positive, NA
crispr_overlap <- crispr[cell_lines, ]

correlations <- cor(prism4, crispr_overlap, use = "pairwise.complete.obs") #pairwsie mean ignore missing values if missing in one or the other
```

Getting the gene names - Diana, Rohan, Andrea
```{r}
gene_names = names(correlations[1,])
```

Maximum value function and loop - Rohan, Andrea, Diana
```{r}
highest = function(metadf, column) {
  max(metadf[,column])
    return(max(metadf[ ,column]))   
}
#function to find the lowest value in a column of a dataframe
```

Getting corresponding row name  (inhibitor names) -Andrea, Diana, Rohan
```{r}
inhibitor_name_finder = function(metadf, column, max_value){
  for (i in 1:length(metadf[ , 1])){
    if (metadf[i,column] == max_value) {
        return(row.names(metadf)[i])
      }
  }
}
#function that looks from top to bottom, in each row, for something that matches the max gene value

Max_gene= 0
inhibitor = gene_names #creating a template vector with specified length (gene_names)
for ( i in 1:length(gene_names)){
 Max_gene[i] = highest(correlations, gene_names[i])
 inhibitor[i] = inhibitor_name_finder(correlations, gene_names[i], Max_gene[i])
  
}
#inhibitor loop uses inhibitor_name_finder function to get the row name that corresponds with maximum gene
#max_gene loop uses function in the correlations matrix for each column and makes the vector max_gene
```

Making a dataframe with the three vectors - Diana, Rohan, Andrea
```{r}
inhibitor_max_gene = data.frame(gene_names, Max_gene, inhibitor)
#putting gene names, min value, and inhibitor together
```

Getting data from new dataframe - Rohan, Andrea, Diana
```{r}
view(table(inhibitor_max_gene$inhibitor))
#frequency table
```

Subsetting for most significant inhibitors - Andrea, Diana, Rohan
```{r}
big_inhibitor = inhibitor_min_gene[inhibitor_min_gene$inhibitor == "BRD-A16035238-001-01-7::2.5::MTS007",]
#looking specifically at the inhibitor that affects the most based on frequency table
```

For class: Where should we explore next? Looking at the most frequent inhibitor or lowest correlation values?

For Andrew: Are these all cancer genes?
What makes a good cancer drug (threshold, versatility of drug, etc.)?
  -0.2 can be a good cut off

Next steps:
Subset for cancer genes?
Assign inhibitors/genes

Interesting gene/inhibitor interactions
CDKN1A associated with tongue carcinoma. BRD-A16035238-001-01-7::2.5::MTS007 is a MDM inhibitor and targets MDM2. 

CHEK2/ATM associated with P53 pathway. BRD-A16035238-001-01-7::2.5::MTS007 is a MDM inhibitor and targets MDM2. 

BMP8B associated with TGF-betal. BRD-K52989797-003-26-4::2.5::HTS is an OCD drug, but has been found to decrease likelihood of brain cancer.

```{r}
drug_name = prism_meta[ ,c("column_name","name","indication")]
drug_name$inhibitor = drug_name$column_name
drug_name = drug_name[ ,c("inhibitor","name","indication")]
named_inhibitor_genes = left_join(inhibitor_max_gene, drug_name, "inhibitor")
```

trying something else
```{r}
cell_lines <- intersect(rownames(prism), rownames(crispr)) #cell lines that are in both dependency and prism

prism_overlap <- prism[cell_lines, inhibitors$column_name]
prism2a = prism_overlap>0
prism3a = prism2*prism_overlap
prism4a = na_if(prism3, 0) #making prism data that is positive, NA
crispr_overlap <- crispr[cell_lines, ]

correlationsa <- cor(prism4, crispr_overlap, use = "pairwise.complete.obs") #pairwsie mean ignore missing values if missing in one or the other
```

We have all been using this generic code to test for our inhibitors
```{r}
library(tidyverse)
library(taigr)
prism <- load.from.taiga(data.name='prism-repurposing-20q2-5e60', data.version=5, data.file='primary-screen-replicate-collapsed-logfold-change')
prism_meta <- load.from.taiga(data.name='prism-repurposing-20q2-5e60', data.version=5, data.file='primary-screen-replicate-collapsed-treatment-info')
crispr <- load.from.taiga(data.name='public-21q2-110d', data.version=12, data.file='Achilles_gene_effect')
library(stats)
expression = load.from.taiga(data.name='public-21q1-4b39',
                             data.version=33,
                             data.file='CCLE_expression',
                             quiet = T)
metadata = load.from.taiga(data.name='public-21q1-4b39', 
                           data.version=33, 
                           data.file='sample_info', 
                           quiet = T)
colnames(expression) = stringr::word(colnames(expression), 1) 
expression = as.data.frame(expression)
expression$DepMap_ID = rownames(expression)
mutation = load.from.taiga(data.name = 'public-21q1-4b39',
                            data.version = 33,
                            data.file = 'CCLE_mutations',
                            quiet = T)
prismdf = as.data.frame(prism)
prismdf$DepMap_ID = rownames(prism)
```

Generic code for find and replace
G E N E
```{r}
#subset for G E N E expression and combine with meta
G E N E = expression[ ,c("G E N E","DepMap_ID")]
meta_G E N E = inner_join(G E N E, metadata, "DepMap_ID") #innerjoining metadata with expression
```
Graphing the expression level based on cancer
```{r}
ggplot(meta_G E N E) + geom_boxplot(mapping = aes(primary_disease, G E N E)) + ggtitle("All Cancer G E N E Expression") + theme_classic()+theme(axis.text.x = element_text(angle = 90))
```
Expression based on mutation status, Similar to KRAS analysis
```{r}
G E N E_Mutation = mutation[mutation$Hugo_Symbol == "G E N E", ]
N_G E N E_mutation = summarize(group_by(G E N E_Mutation, DepMap_ID), N_G E N E_mutation = n())
G E N E_Metadata_expression = full_join(N_G E N E_mutation, meta_G E N E, "DepMap_ID")
G E N E_Metadata_expression$G E N E_mutated =!is.na(G E N E_Metadata_expression$N_G E N E_mutation)
Final_Dataframe_G E N E = G E N E_Metadata_expression[ ,c("DepMap_ID", "G E N E_mutated", "G E N E", "primary_disease")]
###Made data frame with expression of G E N E, mutationstatus, cell line, and cancer sub type
ggplot(Final_Dataframe_G E N E) + geom_boxplot(mapping = aes(G E N E_mutated, G E N E)) + ggtitle("Mutated G E N E Expression") + theme_minimal()
t.test(G E N E ~ G E N E_mutated, Final_Dataframe_G E N E)
table(Final_Dataframe_G E N E$G E N E_mutated)
```
See if the drug has a difference in impact based on cancer type
```{r}
D R U G = prismdf[ ,c("DepMap_ID","I N H I B I T O R N A M E")]
D R U G_meta = inner_join(Final_Dataframe_G E N E, D R U G, "DepMap_ID")
ggplot(D R U G_meta) + geom_boxplot(mapping = aes(primary_disease, `I N H I B I T O R N A M E`)) + ggtitle("All Cancer D R U G Response") + theme_classic()+theme(axis.text.x = element_text(angle = 90))
```
What about expression level?
```{r}
ggplot(D R U G_meta)+geom_point(mapping = aes(G E N E, `I N H I B I T O R N A M E`)) + ggtitle("Drug response based on G E N E expression") + theme_classic()
cor(D R U G_meta$G E N E,D R U G_meta$`I N H I B I T O R N A M E`,use = "pairwise.complete.obs")
```
And Mutation Status?
```{r}
ggplot(D R U G_meta)+geom_boxplot(mapping = aes(G E N E_mutated, `I N H I B I T O R N A M E`)) + ggtitle("Drug response based on G E N E Mutation Status") + theme_classic()
t.test(`I N H I B I T O R N A M E`~ G E N E_mutated, D R U G_meta)
```

