---
title: "Team RAD's second week :)"
output: html_notebook
---
From the last week, we wanted to add more information to the dataframe which contained all genes and the most significant inhibitor- Diana, Rohan, Andrea
```{r}
drug_name = prism_meta[ ,c("column_name","name","indication")]
drug_name$inhibitor = drug_name$column_name
drug_name = drug_name[ ,c("inhibitor","name","indication")]
named_inhibitor_genes = left_join(inhibitor_min_gene, drug_name, "inhibitor")
```

We looked at only drugs that were -0.2 and more negative. Then assigned ourselves to different inhibitor-gene interactions after exploring a bit. 
Rohan- Inhibitor: Mazindol (PTEN gene)
Andrea- Inhibitor: clomipramine (OCD drug)
Diana- Inhibitor: WR99210 (malaria drug impacting several genes)

For the most part, we have been spending much of our time doing exploratory code on genes to find some significance, 

for example, we did similar code to the KRAS problem set
Subset expression for KIRREL1
```{r}
KIRREL1 = expression[ ,c("KIRREL1","DepMap_ID")]
meta_kirrel1 = inner_join(KIRREL1, metadata, "DepMap_ID") #innerjoining metadata with expression
```

Graphing the expression level based on cancer
```{r}
ggplot(meta_kirrel1) + geom_boxplot(mapping = aes(primary_disease, KIRREL1)) + ggtitle("All Cancer KIRREL1 Expression") + theme_minimal()+theme(axis.text.x = element_text(angle = 90))
```
